---
title: "individual2"
author: "Caitlin Fordell"
date: "2/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
##Question 1
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco)
head(choco)
```


```{r}
##Problem 1
hist(choco$Rating, xlab = "Chocolate Rating", main = "Histogram of Chocolate Rating")
```

The histogram of chocolate ratings is unimodal and skewed to the left with a center around 3.25 and outliers around 1, 1.5, 1.75, and 2.

```{r}
boxplot(choco$Rating, main = "Boxplot of Chocolate Rating", ylab = "Rating")
```


The boxplot shows a median around 3.25, the 25th percentile at around 3, and the 75th percentile at 3.75. The boxplot also shows outliers at 1, 1.5, 1.75, and 2 but does not tell how many are at each point.


```{r}
##Plotting cocoa percent and rating
plot(x = choco$Rating, y = choco$Cocoa_Percent, xlab = "Rating", ylab = "Cocoa Percent", main = "Cocoa Percent vs. Chocolate Rating")
```

The graph shows that the lowest ratings were given to the chocolates with a higher cocoa percent. The highest ratings were given to chocolates with about 60 to 80% cocoa. There are outliers that were given ratings of 1 and 1.5. 

```{r}
plot(x = choco$Cocoa_Percent, y = choco$Rating, xlab = "Cocoa Percent", ylab = "Rating", main = "Cocoa Percent vs. Chocolate Rating")
```
There appears to be a negative trend between the rating and the percent of cocoa. As cocoa percent increases, ratings tend to decrease. 

```{r}
##finding correlation between cocoa percent and rating
cor(x = choco$Cocoa_Percent, y = choco$Rating)
```

There is a weak, negative relationship between cocoa percent and chocolate rating. 

```{r}
##histogram of review date
hist(choco$Date, xlab = "Review Date", main = "Histogram of Review Date")
```
Most of the reviews seemed to have been taken around 2014, and the company seemed take less reviews in 2016 and 2020. 

```{r}
##creating a histogram of rating
hist(choco$Rating, xlab = "Rating", main = "Histogram of Rating")
```

The most popular ratings were 2.75 and 3.5, and there appear to be outliers of ratings at 1, 1.5, 1.75, and 2.

```{r}
##creating a summary of ratings
summary(choco$Rating)
```

The minimum rating was 1, the mean rating was 3.184, the median rating was 3.25, and the maximum rating was 4. 
