---
title: "individual2"
author: "Caitlin Fordell"
date: "2/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
##Question 1
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco)
head(choco)
```


1,4,5

```{r}
##Problem 1
hist(choco$Rating, xlab = "Chocolate Rating", main = "Histogram of Chocolate Rating")
```

The histogram of chocolate ratings is unimodal and skewed to the left with a center around 3.25 and outliers around 1, 1.5, 1.75, and 2.

```{r}
boxplot(choco$Rating, main = "Boxplot of Chocolate Rating", ylab = "Rating")
```


The boxplot shows a median around 3.25, the 25th percentile at around 3, and the 75th percentile at 3.75. The boxplot also shows outliers at 1, 1.5, 1.75, and 2 but does not tell how many are at each point.

```{r}
##Problem 4
##Compare country of bean origin and rating

```

```{r}
##Problem 5
##Plotting cocoa percent and rating
plot(x = choco$Rating, y = choco$Cocoa_Percent, xlab = "Rating", ylab = "Cocoa Percent", main = "Cocoa Percent vs. Chocolate Rating")
```

The graph shows that the lowest ratings were given to the chocolates with a higher cocoa percent. The highest ratings were given to chocolates with about 60 to 80% cocoa. There are outliers that were given ratings of 1 and 1.5. 

```{r}
plot(x = choco$Cocoa_Percent, y = choco$Rating, xlab = "Cocoa Percent", ylab = "Rating", main = "Cocoa Percent vs. Chocolate Rating")
```
There appears to be a negative trend between the rating and the percent of cocoa. As cocoa percent increases, ratings tend to decrease. 

```{r}
hist(choco$Date, xlab = "Review Date", main = "Histogram of Review Date")
```

```{r}
hist(choco$Rating, xlab = "Rating", main = "Histogram of Rating")
```


```{r}
##Review Date and Rating
plot(x = choco$Date, y = choco$Rating, xlab = "Review Date", ylab = "Rating", main = "Review Date vs. Chocolate Rating")
```

