---
title: "Team"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
```

## Team Documentation

This is the work on the choco lab from Marcella Anderson, Caitlin Fordell, and Mario Lloyd Galvao-Wilson

### Problem 1

```{r}
##Problem 1
hist(choco$Rating, xlab = "Chocolate Rating", main = "Histogram of Chocolate Rating")
```

The histogram of chocolate ratings is unimodal and skewed to the left with a center around 3.25 and outliers around 1, 1.5, 1.75, and 2.

```{r}
boxplot(choco$Rating, main = "Boxplot of Chocolate Rating", ylab = "Rating")
```


The boxplot shows a median around 3.25, the 25th percentile at around 3, and the 75th percentile at 3.75. The boxplot also shows outliers at 1, 1.5, 1.75, and 2 but does not tell how many are at each point.


### Problem 2

```{r}
lvlChoc <- levels(choco$Location) #defines the levels
typeChoc <- factor(choco$Location, lvlChoc) #defines the factor using the levels

counts <- table(choco$Location)

plt <- barplot(counts, col='steelblue', xaxt="n")
text(plt, par("usr")[3], labels = lvlChoc, srt = 60, adj = c(1.1,1.1), xpd = TRUE, cex=0.7) 

```


### Problem 3



### Problem 4

```{r}
boxplot(choco$Rating ~ typeChoc,  las=2)



```

### Problem 5



