---
title: "Team"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
```

## Team Documentation

This is the work on the choco lab from Marcella Anderson, Caitlin Fordell, and Mario Lloyd Galvao-Wilson

### Problem 1

```{r}
hist(choco$Rating, xlab = "Chocolate Rating", main = "Histogram of Chocolate Rating")
```

The histogram of chocolate ratings is unimodal and skewed to the left with a center around 3.25 and outliers around 1, 1.5, 1.75, and 2.

```{r}
boxplot(choco$Rating, main = "Boxplot of Chocolate Rating", ylab = "Rating")
```


The boxplot shows a median around 3.25, the 25th percentile at around 3, and the 75th percentile at 3.75. The boxplot also shows outliers at 1, 1.5, 1.75, and 2 but does not tell how many are at each point.


### Problem 2

```{r}
lvlChoc <- levels(choco$Location) #defines the levels
typeChoc <- factor(choco$Location, lvlChoc) #defines the factor using the levels

counts <- table(choco$Location)

plt <- barplot(counts, col='steelblue', xaxt="n")
text(plt, par("usr")[3], labels = lvlChoc, srt = 60, adj = c(1.1,1.1), xpd = TRUE, cex=0.7) 

```


### Problem 3
```{r}
##Plotting cocoa percent and rating
plot(x = choco$Rating, y = choco$Cocoa_Percent, xlab = "Rating", ylab = "Cocoa Percent", main = "Cocoa Percent vs. Chocolate Rating")
```

The graph shows that the lowest ratings were given to the chocolates with a higher cocoa percent. The highest ratings were given to chocolates with about 60 to 80% cocoa. There are outliers that were given ratings of 1 and 1.5. 

```{r}
plot(x = choco$Cocoa_Percent, y = choco$Rating, xlab = "Cocoa Percent", ylab = "Rating", main = "Cocoa Percent vs. Chocolate Rating")
```
There appears to be a negative trend between the rating and the percent of cocoa. As cocoa percent increases, ratings tend to decrease. 

```{r}
##finding correlation between cocoa percent and rating
cor(x = choco$Cocoa_Percent, y = choco$Rating)
```

There is a weak, negative relationship between cocoa percent and chocolate rating. 


### Problem 4


```{r}
lvlOrig <- levels(choco$Bean_Origin)
typeOrig <- factor(choco$Bean_Origin, lvlOrig)


boxplot(choco$Rating ~ typeOrig,  las=2)
```

This shows that the bean oragin with the higest average rating is tobago
```{r}
summary(typeOrig)

```
Looking at the summary we see that Tobago only has 2 chocolates which were rated there which may contribute to it's high average. Countries with more data like the Dominican Republic and Ecuador have averages closer to 3.25.


### Problem 5

First we looked at the different reviews and ratings over time

```{r}
##histogram of review date
hist(choco$Date, xlab = "Review Date", main = "Histogram of Review Date")
```

Most of the reviews seemed to have been taken around 2014, and the company seemed take less reviews in 2016 and 2020. 

```{r}
plot(x = choco$Date, y = choco$Rating, xlab = "Review Date", ylab = "Chocolate Rating", main = "Review Date vs. Chocolate Rating")
```

There seems to be a positive trend between review date and chocolate rating, meaning that in the more recent years, the chocolate ratings have been more consistently high.

```{r}

cor(x = choco$Date, y = choco$Rating)
```

There is a weak, positive correlation between chocolate ratings and review date.





