---
title: "Team"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
```

## Team Documentation

This is the work on the choco lab from Marcella Anderson, Caitlin Fordell, and Mario Lloyd Galvao-Wilson

### Problem 1

```{r}
hist(choco$Rating, xlab = "Chocolate Rating", main = "Histogram of Chocolate Rating")
```

The histogram of chocolate ratings is unimodal and skewed to the left with a center around 3.25 and outliers around 1, 1.5, 1.75, and 2.

```{r}
boxplot(choco$Rating, main = "Boxplot of Chocolate Rating", ylab = "Rating")
```


The boxplot shows a median around 3.25, the 25th percentile at around 3, and the 75th percentile at 3.75. The boxplot also shows outliers at 1, 1.5, 1.75, and 2 but does not tell how many are at each point.


### Problem 2

```{r}
lvlChoc <- levels(choco$Location) #defines the levels
typeChoc <- factor(choco$Location, lvlChoc) #defines the factor using the levels

counts <- table(choco$Location)

plt <- barplot(counts, col='steelblue', xaxt="n")
text(plt, par("usr")[3], labels = lvlChoc, srt = 60, adj = c(1.1,1.1), xpd = TRUE, cex=0.7) 

```


### Problem 3
```{r}
##Plotting cocoa percent and rating
plot(x = choco$Rating, y = choco$Cocoa_Percent, xlab = "Rating", ylab = "Cocoa Percent", main = "Cocoa Percent vs. Chocolate Rating")
```

The graph shows that the lowest ratings were given to the chocolates with a higher cocoa percent. The highest ratings were given to chocolates with about 60 to 80% cocoa. There are outliers that were given ratings of 1 and 1.5. 

```{r}
plot(x = choco$Cocoa_Percent, y = choco$Rating, xlab = "Cocoa Percent", ylab = "Rating", main = "Cocoa Percent vs. Chocolate Rating")
```
There appears to be a negative trend between the rating and the percent of cocoa. As cocoa percent increases, ratings tend to decrease. 

```{r}
##finding correlation between cocoa percent and rating
cor(x = choco$Cocoa_Percent, y = choco$Rating)
```

There is a weak, negative relationship between cocoa percent and chocolate rating. 


### Problem 4


```{r}
lvlOrig <- levels(choco$Bean_Origin)
typeOrig <- factor(choco$Bean_Origin, lvlOrig)


boxplot(choco$Rating ~ typeOrig,  las=2)
```

This shows that the bean oragin with the higest average rating is tobago
```{r}
summary(typeOrig)

```
Looking at the summary we see that Tobago only has 2 chocolates which were rated there which may contribute to it's high average. Countries with more data like the Dominican Republic and Ecuador have averages closer to 3.25.


### Problem 5

First we looked at the different reviews and ratings over time

```{r}
##histogram of review date
hist(choco$Date, xlab = "Review Date", main = "Histogram of Review Date")
```

Most of the reviews seemed to have been taken around 2014, and the company seemed take less reviews in 2016 and 2020. 

```{r}
plot(x = choco$Date, y = choco$Rating, xlab = "Review Date", ylab = "Chocolate Rating", main = "Review Date vs. Chocolate Rating")
```

There seems to be a positive trend between review date and chocolate rating, meaning that in the more recent years, the chocolate ratings have been more consistently high.

```{r}

cor(x = choco$Date, y = choco$Rating)
```

There is a weak, positive correlation between chocolate ratings and review date.

We then looked at the different characteristics and which were most used

```{r}
it <- summarise(group_by(choco, Cocoa_Percent), meanRating = mean(Rating))
plot(it$Cocoa_Percent, it$meanRating)

char1head <- head(sort(table(choco$Characteristics1), decreasing = TRUE), 10)
char2head <- head(sort(table(choco$Characteristics2), decreasing = TRUE), 10)
char3head <- head(sort(table(choco$Characteristics3), decreasing = TRUE), 10)

#hist(char1head)
char1l <- c('creamy', 'sandy', 'intense', 'nutty', 'fatty')
char11 <- choco[choco$Characteristics1 == char1l[1], ]
char11m <- mean(char11$Rating)
char12 <- choco[choco$Characteristics1 == char1l[2], ]
char12m <- mean(char12$Rating)
char13 <- choco[choco$Characteristics1 == char1l[3], ]
char13m <- mean(char13$Rating)
char14 <- choco[choco$Characteristics1 == char1l[4], ]
char14m <- mean(char14$Rating)
char15 <- choco[choco$Characteristics1 == char1l[5], ]
char15m <- mean(char15$Rating)

plotd <- c(char11m, char12m, char13m, char14m, char15m)

barplot(plotd, names.arg = char1l, xlab = 'Top 5 Characteristics', ylab = 'Mean Rating', col = 'brown', main = 'Mean Ratings for the Top 5 Characteristics')

```

There did not seem to be a strong difference between the ratings of the top five characteristics. All of them have relatively high average ratings. Creamy is the one that stands out as the top though, making it the most positive characteristic of the top 5. 


